Refinements for open automata

### 2022-06-30 2021-Refinement/paper/refinementarticle.tex
minor change

\begin{definition}[Composition of open automata] \label{Def:CompOA}
The composition of \(A_p = \OAg[p]\) in the hole \(k \in J_c\) of \(A_c = \OAg[c]\) is the OA defined as follows:
\[A_c\subst{A_p}{k} ::=  \OA{S_c \times S_p}{\mpar{s_{0c}, s_{0p}}}{V_c \uplus V_p}{\sigma_{0c} \uplus \sigma_{0p}}{J_p \uplus J_c \setminus \mbrc{k}}{T} \] \text{with }

>>>>

\begin{definition}[Composition of open automata] \label{Def:CompOA}
The composition of \(A_c = \OAg[c]\) in the hole \(k \in J_c\) of  \(A_p = \OAg[p]\) is the OA defined as follows:
\[A_c\subst{A_p}{k} ::=  \OA{S_c \times S_p}{\mpar{s_{0c}, s_{0p}}}{V_c \uplus V_p}{\sigma_{0c} \uplus \sigma_{0p}}{J_p \uplus J_c \setminus \mbrc{k}}{T} \] \text{with }
